% !TEX root = main.tex
% !TEX spellcheck = en-US

\section{Non-malleability of $\marlinprotfs$}
We show that $\marlin$ is forking simulation-extractable. To that end, we show
that $\marlin$ has all the required properties: has unique response property, is
forking special sound, and its simulator can provide indistinguishable proofs
without a trapdoor, just by programming the random oracle.

\subsection{$\marlin$ protocol rolled-out}
$\marlin$ uses R1CS as arithmetization method. That is, the prover given
instance $\inp$ and witness $\wit$ and $|\HHH| \times |\HHH|$ matrices $\vec{A},
\vec{B}, \vec{C}$ shows that $\vec{A} (\inp^\top, \wit^\top)^\top \circ \vec{B}
(\inp^\top, \wit^\top)^\top = \vec{C} (\inp^\top, \wit^\top)^\top$. (Here
$\circ$ is a entry-wise product.)

We assume that the matrices have at most $|\KKK|$ non-zero entries. Obviously,
$|\KKK| \leq |\HHH|^2$. Let $b = 3$, the upper-bound of polynomial evaluations
the prover has to provide for each of the sent polynomials.  Denote by $\dconst$
an upper-bound for $\smallset{|\HHH| + 2b -1, 2 |\HHH| + b - 1, 6 |\KKK| - 6}$.

The idea of showing that the constraint system is fulfilled is as
follows. Denote by $\vec{z} = (\inp, \wit)$. The prover computes polynomials
$\p{z_A} (X), \p{z_B} (X), \p{z_C} (X)$ which encode vectors
$\vec{A} \vec{z}, \vec{B} \vec{z}, \vec{C} \vec{z}$ and have degree $<
|\HHH|$. Importantly, when constrains are fulfilled,
$ \p{z_A} (X) \p{z_B} (X) - \p{z_C} (X) = \p{h_0} (X) \ZERO_\HHH (X)$, for some
$\p{h_0} (X)$ and vanishing polynomial $\ZERO_\HHH (X)$. The prover sends
commitments to these polynomials and shows that they have been computed
correctly. More precisely, it shows that
\begin{equation}
  \label{eq:marlin_eq_2}
\forall \vec{M} \in \smallset{\vec{A}, \vec{B}, \vec{C}},  \forall \kappa \in \HHH,
\p{z_M} (\kappa) = \sum_{\iota \in \HHH} \vec{M}[\kappa, \iota] \p{z}(\iota).
\end{equation}

The ideal verifier checks the following equalities
\begin{equation}
  \label{eq:marlin_ver_eq}
  \begin{aligned}
    \p{h}_3 (\beta_3) \ZERO_\KKK (\beta_3) & = \p{a} (\beta_3) - \p{b} (\beta_3)
    (\beta_3 \p{g_3} (\beta_3) + \sigma_3 / |\KKK|)\\
    \p{r}(\alpha, \beta_2) \sigma_3 & = \p{h_2} (\beta_2) \ZERO_\HHH (\beta_2) +
    \beta_2 \p{g2} (\beta_2) + \sigma_2/|\HHH|\\
    \p{s}(\beta_1) + \p{r}(\alpha, \beta_1) (\sum_M \eta_M \p{z_M} (\beta_1)) -
    \sigma_2 \p{z} (\beta_1) & = \p{h_1} (\beta_1) \ZERO_\HHH (\beta_1) +
    \beta_1
    \p{g_1} (\beta_1) + \sigma_1/|\HHH| \\
    \p{z_A} (\beta_1) \p{z_B} (\beta_1) - \p{z_C} (\beta_1) & = \p{h_0}
    (\beta_1) \ZERO_\HHH (\beta_1)
  \end{aligned}
\end{equation}
where $\p{g_i} (X), \p{h_i} (X)$, $i \in \range{1}{3}$,
$\p{a} (X), \p{b} (X), \sigma_1, \sigma_2, \sigma_3$ are polynomials and
variables required by the sumcheck protocol which allows verifier to efficiently
verify that \cref{eq:marlin_eq_2} holds.
                         

\subsection{Unique response property}
\begin{lemma}
  Let $\PCOM$ be a commitment of knowledge with security $\epsk(\secpar)$,
  $\epsbind(\secpar)$ and has unique response property with security
  $\epsop(\secpar)$. Then probability that a $\ppt$ adversary $\adv$ breaks
  $\marlinprotfs$ $\ur{1}$ property is at most
  $6 \cdot (\epsbind + \epsop + \epsk)$ \michals{8.9}{Do we need to add
    probability that the idealized verifier fails $\epsid$?}
\end{lemma}
\begin{proof}
  As in previous proofs, we show the property by game hops. Let
  $N = \p{g_1}, \p{h_1}, \p{g_2}, \p{h_2}, \p{g_3}, \p{h_3}$. That is, $M$ is a
  set of all polynomials which commitments are send during the protocol after
  Round 1.

  \ncase{Game 0} In this game the adversary wins if it breaks evaluation
  binding, unique opening property, or knowledge soundness of one of commitments
  for polynomials in $N$.

  Probability that a $\ppt$ adversary wins in Game 0, is upper bounded by $6
  \cdot (\epsbind + \epsop + \epsk)$.

  \ncase{Game 1} In this game the adversary additionally wins if it breaks the
  $\ur{2}$ property of the protocol

  \ncase{Game 0 to Game 1} Probability that the adversary wins in
  Game 1 but not in Game 0 is $0$. This is since the polynomials in $N$ are
  uniquely determined. W.l.o.g.~we analyse probability that adversary is able to
  produce two (different) pairs of polynomials $(\p{h_2}, \p{g_2})$ and $(\p{h'_2},
  \p{g'_2})$ such that
  \begin{align*}
    \p{h_2} (X) \ZERO_{\HHH} (X) + X \p{g_2} (X) & = \p{h_2} (X) \ZERO_{\HHH} (X) +
                                                   X \p{g_2} (X)\\
    (\p{h_2} (X) - \p{h'_2} (X)) \ZERO_{\HHH} (X) & = X (\p{g'_2} (X) - \p{g'_2}
    (X)).
  \end{align*}
  Since $\p{h_2}, \p{g_2} \in \FF^{< |\HHH| - 1} [X]$ and
  $\ZERO \in \FF^{|\HHH|} [X]$, LHS has different degree than RHS unless both
  sides have degree $0$. This happens when $\p{h_2} (X) = \p{h'_2} (X)$ and
  $\p{g_2} (X) - \p{g'_2} (X)$.
\end{proof}

\subsection{Forking soundness}
\begin{lemma}
  Assume that an idealised $\marlinprot$ verifier fails with probability at most
  $\epsid(\secpar)$ and probability that a $\ppt$ adversary breaks dlog is
  bounded by $\epsdlog(\secpar)$. Then $\marlinprot$ is
  $(\epsid (\secpar) + \epsdlog (\secpar) + 7 \cdot S \epsh, 2, d + 1)$-forking
  sound, where
  $\epsid (\secpar)$ is probability that the ideal verifier fails, $\epsdlog
  (\secpar)$ is a security of a discrete logarithm, $\epsh (\secpar)$ is
    security of hiding of the polynomial commitment scheme, and $S$ is the
    number of simulator oracle queries made by $\adv$, $S = \poly$.
\end{lemma}
\begin{proof}
 % \michals{8.9}{Need to check the degrees}
  The proof goes similarly to the respective proofs for $\plonk$ and
  $\sonic$. That is, let $\srs$ be $\marlinprot$'s SRS and denote by $\srs_1$
  all SRS's $\GRP_1$-elements. Let $\tdv$ be an algebraic adversary that
  produces a statement $\inp$ and a $(1, \dconst + 1, 1, 1)$-tree of
  acceptable transcripts $\tree$. Note that in all transcripts the instance
  $\inp$, proof elements
  $\sigma_1, \gone{\p{w}(\chi), \p{z_A}(\chi), \p{z_B}(\chi), \p{z_C}(\chi),
    \p{h_0}(\chi), \p{s}(\chi)}, \gone{\p{g_1}(\chi), \p{h_1}(\chi)}$
  % $\sigma_1, \gone{\p{w}(\chi), \p{z_A}(\chi), \p{z_B}(\chi), \p{z_C}(\chi),
  %   \p{h_0}(\chi), \p{s}(\chi)}, \alpha, \eta_A, \eta_B, \eta_C,
  % \gone{\p{g_1}(\chi), \p{h_1}(\chi)}, \beta_1, \sigma_2, \gone{\p{g_2}(\chi),
  % \p{h_2}(\chi)}, \beta_2, \simga_2, \gone{\p{g_3}(\chi), \p{h_3}(\chi)}$
  and challenges $\alpha, \eta_1, \eta_2, \eta_3$ are common as the transcripts
  share the first $3$ messages. The tree branches after the third message of the
  protocol where the challenge $\beta_1$ is presented, thus tree $\tree$ is
  build using different values of $\beta_1$.

  We consider the following games.

  \ncase{Game 0} In this game the adversary wins if all the transcripts it
  produced are acceptable by the ideal verifier,
  i.e.~$\vereq_{\inp, \zkproof}(X) = 0$, cf.~\cref{eq:marlin_ver_eq}, yet the extractor
  fails to extract a valid witness out of them.

  Probability of $\tdv$ winning this game is $\epsid(\secpar)$ as the protocol
  $\marlinprot$, instantiated with the idealised verification equation, is
  perfectly sound except with negligible probability of the idealised verifier
  failure $\epsid(\secpar)$. Hence for a valid proof $\zkproof$ for a statement
  $\inp$ there exists a witness $\wit$, such that $\REL(\inp, \wit)$ holds. Note
  that since the $\tdv$ produces $(\dconst + 1)$ acceptable transcripts for
  different challenges $\beta_1$, it obtains the same number of different
  evaluations of polynomials $\p{z_A}, \p{z_B}, \p{z_C}$.

  Since the transcripts are acceptable by an idealised verifier, the equality
  $\p{z_A} (X) \p{z_B} (X) - \p{z_C} (X) = \p{h_0} (X) \ZERO_\HHH (X)$ holds and
  each of $\p{z}_M$, $M \in \smallset{A, B, C}$, has been computed
  correctly. Hence, $\p{z_A}, \p{z_B}, \p{z_C}$ encodes the valid witness for
  the proven statement. Since $\p{z_A}, \p{z_B}, \p{z_C}$ are of degree at most
  $d$ and there is more than $(\dconst + 1)$ their evaluations
  known, $\extt$ can recreate their coefficients by interpolation and reveal the
  witness with probability $1$. Hence, the probability that extraction fails in
  that case is upper-bounded by probability of an idealised verifier failing
  $\epsid(\secpar)$, which is negligible.

  \ncase{Game 1} In this game the adversary additionally wins if it produces a
  transcript in $\tree$ such that $\vereq_{\inp, \zkproof}(\chi) = 0$, but
  $\vereq_{\inp, \zkproof}(X) \neq 0$. That is, the ideal verifier does not
  accept the proof, but the real verifier does.

  \ncase{Game 0 to Game 1} Assume the adversary wins in Game 1, but
  does not win in Game 0. We show that such adversary may be used to break the
  $\dlog$ assumption. More precisely, let $\tdv$ be an adversary that for
  relation $\REL$ and randomly picked $\srs \sample \kgen(\REL)$ produces a tree
  of acceptable transcripts such that the winning condition of the game
  holds. Let $\rdvdlog$ be a reduction that gets as input an
  $(\dconst, 1)$-dlog instance $\gone{1, \ldots, \chi^\dconst}, \gtwo{1, \chi}$ and
  is tasked to output $\chi$. The reduction proceeds as follows---it gives the
  input instance to the adversary as the SRS. Let $(1, \tree)$ be the output
  returned by $\adv$. Let $\inp$ be a relation proven in $\tree$.  Consider a
  transcript $\zkproof \in \tree$ such that $\vereq_{\inp, \zkproof}(X) \neq 0$,
  but $\vereq_{\inp, \zkproof}(\chi) = 0$. Since the adversary is algebraic, all
  group elements included in $\tree$ are extended by their representation as a
  combination of the input $\GRP_1$-elements. Hence all coefficients of the
  verification equation polynomial $\vereq_{\inp, \zkproof}(X)$ are known and
  $\rdvdlog$ can find its zero points. Since
  $\vereq_{\inp, \zkproof}(\chi) = 0$, the targeted discrete log value $\chi$ is
  among them.  Hence, the probability that this event happens is upper-bounded
  by $\epsdlog(\secpar)$.

  \ncase{Game 2} In this game the adversary additionally wins if at least one of
  the commitments $\gone{\p{z}_A (\chi), \p{z}_B (\chi)}$ utilizes a commitment
  that comes from a simulated proof; for example, $\adv$ could compute its
  commitment to $\p{z}_A(X)$ as follows: it picks a polynomial $\p{p} (X)$,
  computes $\gone{\p{p} (\chi)}$, and outputs commitment
  $\gone{\p{c} (\chi)} = \gone{\p{p} (\chi)} + c$, where $c$ is a commitment
  output by a simulator. In the following, w.l.o.g, we assume that $\adv$ uses
  some simulated element to compute commitment $\gone{\p{z}_A (\chi)}$.

  \ncase{Game 1 to Game 2} Given adversary $\adv$ that wins in Game 2, but not
  in Game 1, we show a reduction $\rdv$ that uses $\adv$ and $\tdv$ to break
  hiding property of the commitment scheme. $\rdv$ proceeds as follows:
  \begin{enumerate}
  \item Given polynomial commitment SRS $\srs_{\PCOMs}$, produce $\marlin$'s SRS
    $\srs$ similarly to Game 1. 
  \item Pick random polynomials
    $\p{p} (X), \p{p'} (X) \in \FF^{< |\dconst|} (X)$, hiding parameter
    $k = 2$ and send them to the polynomial commitment challenger $\cdv$.
  \item From the challenger get the challenge commitment $c$.
  \item Let $S$ be the upper bound on the number of simulator oracles queries
    the adversary can make. 
  \item Guess which simulator's response is going to be used by $\adv$ in its
    proof. Let $s$ be the index of this response.
  \item Guess which of the simulated polynomials in response $s$ will be
    used. Let $i$ be the index of this polynomial.
  \item Let $\tdv'$ be an algorithm that behaves exactly as $\tdv$, except when
    $\adv$ asks for $s$-th simulated proof, $\tdv'$'s internal procedure $\bdv'$
    provides $\adv$ with a simulated proof such that instead of commitment
    $\p{z}_A (\chi)$ it gives $c$. 
  \item Start $\tdv'(\adv, \srs)$ and get the tree $\tree$.
  % \item If indices $s$ or $i$ have not been guessed correctly, rewind $\adv$ to
  %   the beginning and pick new $s$ and $i$. Since $S = \poly$ probability that
  %   the correct $s$ will be guessed in polynomial time is overwhelming. That is,
  %   the reduction works in expected polynomial time. Similarly, $i$ takes values
  %   from $\range{1}{3}$, hence probability that $\rdv$ guesses $i$ in polynomial
  %   time is overwhelming. 
  \item Since $\tree$ contains $(\dconst + 1)$ evaluations of $\p{z}_A (X)$, the
    polynomial can be reconstructed.
  \item Since $\adv$ is algebraic, $\rdv$ learns composition of $\p{z}_A (X)$
    in the $\srs$ and simulated elements.
  \item Hence $\rdv$ learns whether $c$ is a commitment to $\p{p} (X)$ or
    $\p{p'} (X)$.
  \item $\rdv$ returns its guessing bit to $\cdv$.
  \end{enumerate}

  \ncase{Game 3} In this game the adversary additionally wins if one of the
  commitments
  $\gone{\p{z}_C (\chi), \p{s} (\chi), \p{h_0} (\chi), \p{g_1} (\chi), \p{g_2}
    (\chi)}$ comes from a simulated proof.

  \ncase{Game 2 to Game 3} Given adversary $\adv$ that wins in Game 3, but not
  in Game 2, we show a reduction $\rdv$ that uses $\adv$ and $\tdv$ to break
  hiding property of the commitment scheme.  W.l.o.g.~we assume that the
  polynomial that utilizes a simulated element is $\p{z}_C$. $\rdv$ proceeds as
  follows:
  \begin{enumerate}
  \item Guess the simulation query index $s$ the polynomial(s) come from.
  \item Pick random $\beta_1$ and compute polynomial $\p{z}_C (X)$ as a
    simulator would compute.
  \item Produce two random polynomials $\p{p_0} (X)$ and $\p{p_1} (X)$ and send
    them to the challenger $\cdv$. Get commitment $c$.
  \item Let $\tdv'$ be an algorithm that behaves exactly as $\tdv$, except when
    $\adv$ asks for $s$-th simulated proof, $\tdv'$'s internal procedure $\bdv'$
    provides $\adv$ with a simulated proof such that:
    \begin{enumerate}
    \item Start making the simulated proof as a trapdoor-less simulator would.
    \item Get evaluation $p_{\beta_1} = \p{p_b} (\beta_1)$, i.e.~evaluate the polynomial
      in $c$ at $\beta_1$.
    \item Let $\tilde{z_C}$ be the evaluation of the simulated $\p{z}_C (\beta)$.
    \item Pick $r$ such that $p_{\beta_1} + r = \p{z}_C (\beta)$.
    \item For the commitment of $\p{z}_C (X)$ output $c' = c + \gone{r}$.
    \item Compute the rest of the simulated proof as a simulator would.
    \end{enumerate}
  \item Let $\tdv'$ be an algorithm that behaves exactly as $\tdv$, except when
    $\adv$ asks for $s$-th simulated proof, $\tdv'$'s internal procedure $\bdv'$
    provides $\adv$ with a simulated proof such that instead of a simulated
    $\gone{\p{z}_C (\chi)}$ it gives $c'$.
  \item Start $\tdv'(\adv, \srs)$ and get the tree $\tree$.
  % \item If index $s$ has not been guessed correctly, rewind $\adv$ to
  %   the beginning and pick new $s$. Since $S = \poly$ probability that
  %   the correct $s$ will be guessed in polynomial time is overwhelming. That is,
  %   the reduction works in expected polynomial time. 
  \item Since $\tree$ contains $(\dconst + 1)$ evaluations of $\p{z}_C (X)$, the
    polynomial can be reconstructed.
  \item Since $\adv$ is algebraic, $\rdv$ learns composition of $\p{z}_C (X)$ in
    the $\srs$ and simulated elements.
  \item Hence $\rdv$ learns whether $c$ is a commitment to $\p{p} (X)$ or
    $\p{p'} (X)$.
  \item $\rdv$ returns its guessing bit to $\cdv$.
  \end{enumerate}
\end{proof}

\subsection{Honest-verifier zero knowledge}
\begin{lemma}
  \label{lem:marlin_hvzk}
  $\marlinprot$ is honest verifier zero-knowledge.
\end{lemma}
\begin{proof}
The simulator follows the protocol except it picks the challenges $\alpha,
\eta_A, \eta_B, \eta_C, \beta_1, \beta_2, \beta_3$ before it picks polynomials
it sends.

First, it picks $\p{\tilde{z}}_A (X)$, $\p{\tilde{z}}_B (X)$ at random and
$\p{\tilde{z}}_C (X)$ such that
$\p{\tilde{z}}_A (\beta_1) \p{\tilde{z}}_B (\beta_1) = \p{\tilde{z}}_C
(\beta_1)$.  Given the challenges and polynomials $\p{\tilde{z}}_A (X)$,
$\p{\tilde{z}}_B (X)$, $\p{\tilde{z}}_C (X)$ the simulator computes
$\sigma_1 \gets \sum_{\kappa \in \HHH} \p{s}(\kappa) + \p{r}(\alpha, X) (\sum_{M
  \in \smallset{A, B, C}}\eta_M \p{\tilde{z}}_M(X)) - \sum_{M \in \smallset{A,
    B, C}} \eta_M \p{r}_M (\alpha, X) \p{\tilde{z}} (X)$.

Then the simulator starts the protocol and follows it, except it programs the
random oracle that on partial transcripts it returns the challenges picked by
$\simulator$.
\end{proof}

\subsection{From forking soundness and unique response property to forking
  simulation extractability of $\marlinprotfs$}
\begin{corollary}
  Assume that $\marlinprot$ is $\ur{1}$ with security
  $\epsur(\secpar) = 6 \cdot (\epsbind + \epsop + \epsk)$, and forking-sound
  with security $\epsfor (\secpar)$. Let $\ro\colon \bin^* \to \bin^\secpar$ be a
  random oracle. Let $\advse$ be an algebraic adversary that can make up to $q$
  random oracle queries, up to $S$ simulation oracle queries, and outputs an
  acceptable proof for $\marlinprotfs$ with probability at least
  $\accProb$. Then $\marlinprotfs$ is forking simulation-extractable with
  extraction error $\eta = \epsur(\secpar)$. The extraction probability
  $\extProb$ is at least
\[
  \extProb \geq \frac{1}{q^{\dconst}} (\accProb - \epsur(\secpar))^{\dconst + 1}
  - \eps(\secpar).
	\]
	for some negligible $\eps(\secpar)$, $\dconst$ being, the upper bound of
  constrains of the system.
  \[
    \extProb \geq q^{-(\dconst - 1)} (\accProb - 6 \cdot (\epsbind + \epsop +
    \epsk))^{\dconst} -\eps(\secpar)\,.
\]
\end{corollary}

\section{Further work}
We identify a number of problems which we left as further work. First of all,
the generalised version of the forking lemma presented in this paper can be
generalised even further to include protocols where forking soundness holds for
protocols where $\extt$ extracts a witness from a $(n_1, \ldots, n_\mu)$-tree of
acceptable transcripts, where more than one $n_j > 1$. I.e.~to include
protocols that for witness extraction require transcripts that branch at more
than one point.

Although we picked $\plonk$ and $\sonic$ as examples for our framework, it is
not limited to SRS-based NIZKs. Thus, it would be interesting to apply it to
known so-called transparent zkSNARKs like Bulletproofs \cite{SP:BBBPWM18},
Aurora \cite{EC:BCRSVW19} or AuroraLight \cite{EPRINT:Gabizon19a}.

Since the rewinding technique and the forking lemma used to show simulation
extractability of $\plonkprotfs$ and $\sonicprotfs$ come with security loss,
it would be interesting to show SE of these protocols directly in the
algebraic group model.

Although we focused here only on zkSNARKs, it is worth to
investigating other protocols that may benefit from our framework, like
e.g.~identification schemes.

Last, but not least, this paper would benefit greatly if a more tight version
of the generalised forking lemma was provided. However, we have to note here
that some of the inequalities used in the proof are already tight, i.e.~for
specific adversaries, some of the inequalities are already equalities.
